\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory

### 2025-06-24 2nd report/2report.tex
New

\begin{document}
\setbeamertemplate{itemize item}{\normalsize\textbullet}
\begin{frame} % ← 不使用 [plain]，保留 Madrid 顶部蓝条
  \titlepage
\end{frame}
\section{Motivation}
\begin{frame}{Why We Study Scattering Amplitudes?}
  \begin{enumerate}
    \item \textbf{Bridge between theory and experiment}
    \begin{itemize}
      \item Core prediction targets for high-energy collider experiments such as the LHC , especially for high multiplicity amplitudes.
      \item Any new theory (SUSY, GUTs, extra dimensions) must predict observable cross sections
    \end{itemize}
    \pause
    \item \textbf{Reveal deep structures of quantum field theory}
    \begin{itemize}
      \item Amplitudes exhibit hidden symmetries (e.g., dual conformal, Yangian) not visible in the Lagrangian
      \item These symmetries suggest deeper theoretical frameworks, such as amplituhedra or AdS/CFT correspondence
    \end{itemize}
  \end{enumerate}
\end{frame}

@@

        \end{tikzpicture}
    \end{center}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}  
    \end{itemize}
\end{frame}

\begin{frame}
    Here I show the concrete computation process 
    \begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{6pt.eps}
    \end{figure}
    \vspace{-1em}
    \begin{align*}
    A_1&=\frac{(-1)\asqu{\hat{2}6}\asqu{16}}{\mdavg{25}{56}\!\avg{61}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
    &=\frac{\asqu{26}\avg{16}}{\mdavg{25}{56}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[34]^3}{[4\hat{I}][\hat{I}3]}\notag\\
    &=\frac{\asqu{26}\avg{16}\bcancel{[34]^3}\bcancel{\avg{42}}}{\mdavg{25}{56}\!\mdavg{41}{32}\!\avg{43}\bcancel{[43][43][34]}\bcancel{\avg{24}}}\notag\\
    &=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
    \end{align*}
\end{frame}
\begin{frame}
    \begin{itemize}
        \item Compact formula for general case
        \begin{equation*}
            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
        \end{equation*} 
        \begin{minipage}{0.7\textwidth}
            \raggedright  % 或者 \centering 或 \raggedleft
            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
            $\star$: \,Order for gauge group 1\\
            $\ast$: \,Order for gauge group 2 
            \end{minipage}

>>>>

\begin{document}
\setbeamertemplate{itemize item}{\normalsize\textbullet}
\begin{frame} % ← 不使用 [plain]，保留 Madrid 顶部蓝条
  \titlepage
\end{frame}
\section{Motivation}
\begin{frame}{Why We Study Scattering Amplitudes?}
  \begin{enumerate}
    \item \textbf{Bridge between theory and experiment}
    \begin{itemize}
      \item Core prediction targets for high-energy collider experiments such as the LHC , especially for high multiplicity amplitudes.
      \item Any new theory (SUSY, GUTs, extra dimensions) must predict observable cross sections
    \end{itemize}
    \pause
    \item \textbf{Reveal deep structures of quantum field theory}
    \begin{itemize}
      \item Amplitudes exhibit hidden symmetries (e.g., dual conformal, Yangian) not visible in the Lagrangian
      \item These symmetries suggest deeper theoretical frameworks, such as amplituhedra or holographic principle (celestial duality).
    \end{itemize}
  \end{enumerate}
\end{frame}

@@

        \end{tikzpicture}
    \end{center}
    The color factor here have special form like
    \begin{equation*}
         (T_1^{a_1}T_1^{a_2}\cdots T_1^{a_{n_1}})_{ij}(T_2^{b_1}T_2^{b_2}\cdots T_2^{b_{n_2}})_{\bar{j}\bar{i}}
    \end{equation*}
     we can notice that the relative order between two gauge group do not affect the color structure, but the
    order inside the gauge group matters.
\end{frame}

\begin{frame}
    So we introduce the \textbf{OPP (Order Preserving Permutation)}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1^\Phi2^{\Phi^\dagger}3_1^+4_1^+5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}  
    \end{itemize}
\end{frame}
\begin{frame}
    Here I show the concrete computation process 
    \begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{6pt.eps}
    \end{figure}
    \vspace{-1em}
    \begin{align*}
    A_1&=\frac{(-1)\asqu{\hat{2}6}\asqu{16}}{\mdavg{25}{56}\!\avg{61}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
    &=\frac{\asqu{26}\avg{16}}{\mdavg{25}{56}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[34]^3}{[4\hat{I}][\hat{I}3]}\notag\\
    &=\frac{\asqu{26}\avg{16}\bcancel{[34]^3}\bcancel{\avg{42}}}{\mdavg{25}{56}\!\mdavg{41}{32}\!\avg{43}\bcancel{[43][43][34]}\bcancel{\avg{24}}}\notag\\
    &=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
    \end{align*}
\end{frame}
\begin{frame}
    \begin{itemize}
        \item Compact formula for general case
        \begin{equation*}
            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
        \end{equation*} 
        \begin{minipage}{0.7\textwidth}
            \raggedright  % 或者 \centering 或 \raggedleft
            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
            $\star$: \,Order for gauge group 1\\
            $\ast$: \,Order for gauge group 2 
            \end{minipage}
